\documentclass[11pt]{article}
%
\include{macros}
\usepackage{graphicx}
\usepackage{pxfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{epstopdf}
\usepackage{fullpage}
\usepackage{epic}
\usepackage{eepic}

\begin{document}

\title{CS5625 Final Project Proposal}
\author{Michael Flashman \\ mtf53@cornell.edu \and Tianhe Zhang \\ tz249@cornell.edu\\}
\date{\today}
\maketitle


\section{Overview}
We propose a simple  game based the short play \textit{Act Without Words I}, by Samuel Becket.   
The setting for the game is sandy dessert under on blazing .  In the middle of this dessert scene stands a palm tree, and a pile of perfect spheres.  The premise of the game is to launch these spheres off into the distance using the palm tree as an impromptu catapult.   When the sphere hits the ground, something or nothing happens. 

\section{Game design}
% talk about the game

\section{Technical Components}
The main challenge for our game is how we create a real time physical interactive object such as our palm tree. We would like to experiment how the tree skeleton mesh interacts with different kinds of forces. In order to this, we are going to explore a third party physical engine. Other tasks includes how we can build the mesh for the tree model procedurally according to the skeleton mesh.\\

Another challenge is to make the tree look plausible. We would like to explore the hair optimization method described in [1] and use it to simulate the tree leaves and fronds. In this way, we make our tree model more efficient.\\

We also plan to implement other techniques if time allowed. For example, we can implement a normal/relief mapping for the bark on the trunk. We would also want to explore the wind model described in [2] so that we can see how the palm tree interacts with the wind.

%\begin{enumerate}
\section{Tentative Schedule}
\begin{itemize}
\item{Week 1: April 1 - April 7}

\begin{enumerate}
\item{Tree model: build a skeleton mesh procedurally for the palm tree rendering and physical simulation.}
\item{Explore physics engine and try to connect to our base code.}
\end{enumerate}

\item{Week 2: April 8 - April 14}

\begin{enumerate}
\item{Tree model: build the basic tree mesh procedurally by using the skeleton mesh.}
\item{Terrain: build a basic terrain using subdivision surface.}

\end{enumerate}

\item{Week 3: April 15 - April 21}

\begin{enumerate}
\item{Optimize tree simulation by using the interpolation of leaves and fronds based on the hair model.}

\end{enumerate}

\item{Week 4: April 22 - April 28}

\begin{enumerate}
\item{Apply the physics simulation to the skeleton mesh.}
\item{Apply certain techniques to make the tree look nice. e.g. Normal mapping for the trunck.}
\end{enumerate}

\item{Week 5: April 29 - May 5}

\begin{enumerate}
\item{Game implementation: Shooting a rock to the desert.}

\end{enumerate}

\item{Week 6: May 10 - May 15}

\begin{enumerate}
\item{Implement wind simulation similar to the method described in Chapter 6. GPU-Generated Procedural Wind Animations for Trees from Gem3. }
\end{enumerate}

\end{itemize}

\section{Citations}
\begin{thebibliography}{11}

\bibitem{1}
GPU gems 2 : programming techniques for high-performance graphics and general-purpose
computation / edited by Matt Pharr ; Randima Fernando, series editor.

\bibitem{2}
GPU gems 3 : Chapter 6. GPU-Generated Procedural Wind Animations for Trees by Renaldas Zioma 


\bibitem{3}
Di Giacomo, Thomas, Stéphane Capo, and François Faure. 2001. "An Interactive Forest." In Proceedings of the Eurographic Workshop on Computer Animation and Simulation, pp. 65–74.

\bibitem{4}
Harker, George. 2002. "Animation of Trees in the Wind: Efficient and Believable Tree Motion." Submission for SIGGRAPH 2002.

\bibitem{5}
Harris, Mark J. 2004. "Fast Fluid Dynamics Simulation on the GPU." In GPU Gems, edited by Randima Fernando, pp. 637–665. Addison-Wesley.

\bibitem{6}
Kanda, Hitoshi, and Jun Ohya. 2003. "Efficient, Realistic Method for Animating Dynamic Behaviors of 3D Botanical Trees." In Proceedings of the IEEE International Conference on Multimedia and Expo 2003, vol. 2, pp. 89–92.

\bibitem{7}
NVIDIA Corporation. 2004. "Matrix Palette Skinning" NVIDIA SDK White Paper. Available online at %http://download.nvidia.com/developer/SDK/Individual_Samples/DEMOS/Direct3D9/src/HLSL_PaletteSkin/docs/HLSL_PaletteSkin.pdf.

\bibitem{8}
Ota, Shin, et al. 2003. "1/fb Noise-Based Real-Time Animation of Trees Swaying in Wind Fields." In Proceedings of Computer Graphics International 2003, pp. 52–60.

\bibitem{9}
Stam, Jos. 1997. "Stochastic Dynamics: Simulating the Effects of Turbulence on Flexible Structures." Computer Graphics Forum 16(3), pp. 159–164.

\bibitem{10}
Watt, Alan, and Mark Watt. 1992. Advanced Animation and Rendering Techniques. Addison-Wesley. See pp. 363–364.

\bibitem{11}
Wejchert, Jakub, and David Haumann. 1991. "Animation Aerodynamics." In Proceedings of the 18th Annual Conference on Computer Graphics and Interactive Techniques, pp. 19–21.

\bibitem{12}
Green, Simon. 2004. "Real-Time Approximations to Subsurface Scattering." In GPU Gems, edited by Randima Fernando, pp. 263–278. Addison-Wesley.

\bibitem{13}
Jakobsen, Thomas. 2003. "Advanced Character Physics." IO Interactive.

\bibitem{14}
Kim, T.-Y., and U. Neumann. 2001. "Opacity Shadow Maps." In Proceedings of SIGGRAPH 2001, pp. 177–182.

\bibitem{15}
Marschner, S. R., H. W. Jensen, M. Cammarano, S. Worley, and P. Hanrahan. 2003. "Light Scattering from Human Hair Fibers." ACM Transactions on Graphics (Proceedings of SIGGRAPH 2003) 22(3), pp. 780–791.

\bibitem{16}
McCool, Michael D., Jason Ang, and Anis Ahmad. 2001. "Homomorphic Factorizations of BRDFs for High-Performance Rendering." In Proceedings of SIGGRAPH 2001, pp. 171–178.
\end{thebibliography}
\end{document}
